### 2017-12-18 manuscript.rmd
photo credit Bathyphysa
updated specimen table

The Calycophorae and Clade A each have very different arangements of monoecy, providing evidence for multiple gains of monoecy. In both the Calycophorae and Clade A, male and female gonophores are located within the same colony. In calycophorans, each cormidium (a single reiterated sequence of zooids along the stem, see Fig. 2) bears either male or female zooids. In this form of monoecy, the male and female cormidia can either be in an alternating pattern, or there can be several male or female cormidia in a row. In either case, male and female zooids are found at the same corresponding locations within the cormidia. In Clade A, however, male and female zooids are found within the same cormidium.In these species, the male and female zooids are placed at very different but well defined locations within the cormidium.

@@

This work was supported by the National Science Foundation (DEB-1256695 and the Waterman Award). Sequencing at the Brown Genomics Core facility was supported in part by NIH P30RR031153 and NSF EPSCoR EPS-1004057. Data transfer was supported by NSF RII-C2 EPS-1005789. Analyses were conducted with computational resources and services at the Center for Computation and Visualization at Brown University, supported in part by the NSF EPSCoR EPS-1004057 and the State of Rhode Island. SOWHAT analyses were carried out on the Odyssey cluster supported by the FAS Division of Science, Research Computing Group at Harvard University -- we thank Cassandra Extavour for use of the Harvard cluster. We also thank the MBARI crews and ROV pilots for collection of the specimens.

>>>>

The Calycophorae and Clade A each have very different arrangements of male and female gonophores, providing evidence for multiple gains of monoecy. In both the Calycophorae and Clade A, male and female gonophores are located within the same colony. In calycophorans, each cormidium (a single reiterated sequence of zooids along the stem, see Fig. 2) bears either male or female zooids. In this form of monoecy, the male and female cormidia can either be in an alternating pattern, or there can be several male or female cormidia in a row. In either case, male and female zooids are found at the same corresponding locations within the cormidia. In Clade A, however, male and female zooids are found within the same cormidium.In these species, the male and female zooids are placed at very different but well defined locations within the cormidium.

@@

This work was supported by the National Science Foundation (DEB-1256695 and the Waterman Award). Sequencing at the Brown Genomics Core facility was supported in part by NIH P30RR031153 and NSF EPSCoR EPS-1004057. Data transfer was supported by NSF RII-C2 EPS-1005789. Analyses were conducted with computational resources and services at the Center for Computation and Visualization at Brown University, supported in part by the NSF EPSCoR EPS-1004057 and the State of Rhode Island. SOWHAT analyses were carried out on the Odyssey cluster supported by the FAS Division of Science, Research Computing Group at Harvard University -- we thank Cassandra Extavour for use of the Harvard cluster. We thank Rob Sherlock for providing the *Bathyphysa conifera* photograph. We also thank the MBARI crews and ROV pilots for collection of the specimens.
